Learning and Recognition of \strips\ Action Models from State Observations \\ Action Model Recognition from State Observations via Planning

### 2018-01-22 doc/ijcai-18/observations-learning.tex
added results for the 5 last domains

\begin{table}
		\begin{center}
			\begin{tabular}{l|l|l|l|}
				& $\delta(\Xi,\mathcal{O})$ & $\delta(\Xi,*)$ & $P(\mathcal{O}|\Xi)$ \\
				\hline
				block & 0 & 90 & 1.0 \\
				ferry & 2 & 69 & 0.97 \\
				grid & 42 & 153 & 0.73 \\
				gripper & 2 & 30 & 0.93 \\
				hanoi & 1 & 63 & 0.98 \\
				miconic & 3 & 72 & 0.96 \\
				npuzzle & 2 & 24 & 0.92 \\
				transport & 4 & 78 & 0.95 \\
				visitall & 2 & 24 & 0.92 \\
				zenotravel & 3 & 63 & 0.95 \\
				\hline
				\bf  & - & - & - \\
			\end{tabular}
		\end{center}
	\caption{\small $P(\mathcal{O}|\Xi)=1-\frac{\delta(\Xi,\mathcal{O})}{\delta(\Xi,*)}$}
	\label{fig:observationstest}                
\end{table}

>>>>

\begin{table}
		\begin{center}
			\begin{tabular}{l|l|l|l|}
				& $\delta(\Xi,\mathcal{O})$ & $\delta(\Xi,*)$ & $P(\mathcal{O}|\Xi)$ \\
				\hline
				block & 0 & 90 & 1.0 \\
				driverlog & 5 & 144 & 0.97 \\
				ferry & 2 & 69 & 0.97 \\
				floortile & 34 & 342 & 0.90 \\
				grid & 42 & 153 & 0.73 \\
				gripper & 2 & 30 & 0.93 \\
				hanoi & 1 & 63 & 0.98 \\
				hiking & 69 & 174 & 0.60 \\
				miconic & 3 & 72 & 0.96 \\
				npuzzle & 2 & 24 & 0.92 \\
				parking & 5 & 111 & 0.95 \\
				satellite & 24 & 75 & 0.68 \\
				transport & 4 & 78 & 0.95 \\
				visitall & 2 & 24 & 0.92 \\
				zenotravel & 3 & 63 & 0.95 \\
				\hline
				\bf  & - & - & - \\
			\end{tabular}
		\end{center}
	\caption{\small $P(\mathcal{O}|\Xi)=1-\frac{\delta(\Xi,\mathcal{O})}{\delta(\Xi,*)}$}
	\label{fig:observationstest}                
\end{table}
